\chapter*{Summary}
\setheader{Summary}

This report describes the process of finding a solution to the problem: ``How can the existing FeedbackFruits platform be extended in such a way that everyone in the FeedbackFruits community can contribute to the software development process?'' This process consist of a research phase and an implementation phase. The conclusions of the research were processed into a set of requirements for a solution. These requirements emphasises the central role of communication in community engagement. Additionally, the research shows that there are no modern tools for requirements engineering, a process centered around decomposing a problem into smaller problems that can be solved in order to find a solution for the bigger problem.

The solution that was implemented during this project facilitates collaboration between technical and non-technical users by integrating existing software development tools and offering their functionalities in an interface that is more user-friendly to non-technical users. Users have the ability to indicate what they would like to see in the FeedbackFruits and share this on social media such as Facebook and Twitter. The solution also provides a centralised means of communication between all supporters of an extension to the FeedbackFruits platform.

The implementation does not cover all of the requirements specified as a result of the research. Although the team would like to have delivered a complete solution, they feel the extensibility of the implementation and the broad scope of the research make up for the requirements that were not implemented during this project.